\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-09 appendix-2.Rmd
Figure legends corrected

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5. Three items: 25, 04, 01 carriedlow information. However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.  Item 01 and 25 had relatively flat information curve with a peak lower than .20'', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 1200)
```

>>>>

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5. Three items: 25, 04, 01 carriedlow information. However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.  Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 1200)
```

### 2022-01-09 manuscript.Rmd
Figure legends corrected

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}

@@

```{r iteminfo, eval=FALSE, warning=FALSE, include=FALSE}
#Not used in the manuscript

F1_item1<- plot(F1_fit, type = "infotrace", 
                    facet_items = T, which.items = 1, main = "")

F1_item2 <- plot(F1_fit, type = "infotrace", 
     facet_items = T, which.items = 2,main = "")

F1_item3 <- plot(F1_fit, type = "infotrace", 
     facet_items = T, which.items = 3,main = "")

F2_item1 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 1,main = "")
F2_item2 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 2,main = "")
F2_item3 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 3,main = "")
F2_item4 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 4,main = "")
F2_item5 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 5,main = "")
F2_item6 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 6,main = "")

F3_item1 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 1,main = "")
F3_item2 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 2,main = "")

F3_item3 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 3,main = "")
F3_item4 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 4,main = "")
F3_item5 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 5,main = "")

F4_item1 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
F4_item2 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
F4_item3 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
F4_item4 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")

F5_item1 <- plot(F5_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
F5_item2 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
F5_item3 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
F5_item4 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
F5_item5 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 5,main = "")

F1title <- ggdraw() + 
  draw_label(
    "F1: Wearing blue light filters",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F2title <- ggdraw() + 
  draw_label(
    "F2: Spending time outdoors",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F3title <- ggdraw() + 
  draw_label(
    "F3: Using phone and smart-watch in bed",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F4title <- ggdraw() + 
  draw_label(
    "F4: Using light before bedtime",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F5title <- ggdraw() + 
  draw_label(
    "F5: Using light...daytime",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

f1itemplot <- plot_grid(F1_item1, F1_item2,F1_item3,
          labels = "AUTO", label_size = 10,align = "v")
f2itemplot <- plot_grid(F2_item1, F2_item2,F2_item3,F2_item4,F2_item5,F2_item6,
           label_size = 10,align = "v")
f3itemplot <- plot_grid(F3_item1, F3_item2,F3_item3,F3_item4,F3_item5,
           label_size = 10,align = "v")
f4itemplot <- plot_grid(F4_item1, F4_item2,F4_item3,F4_item4,
          labels = "AUTO", label_size = 10,align = "v")

f5itemplot <- plot_grid(F5_item1, F5_item2,F5_item3,F5_item4,F5_item5,
          label_size = 10,align = "v")
```

@@

```{r inteminfoggplo2com, eval=FALSE, include=FALSE}
#Victimization
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

>>>>

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pain 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}

@@

@@

```{r inteminfoggplo2com, eval=FALSE, include=FALSE}

pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))
